### 2024-02-23 arxiv_final_version/localpsf.tex
add folder for arxiv version of paper

% SIAM Article Template
\documentclass[review,onefignum,onetabnum]{siamart190516}

@@

\begin{figure}
	\centering
	{
		\begin{tabular}{ccc}
			& $T=0.5$ 
			& $T=2.0$ \\
			$\kappa=1.0$e${-4}$  & \includegraphics[scale=0.12, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-4.png} 
			& \includegraphics[scale=0.12, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-4.png} \\
			$\kappa=1.0$e${-3}$ & \includegraphics[scale=0.12, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-3.png} 
			& \includegraphics[scale=0.12, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-3.png}
		\end{tabular}
	}
	\caption{(Advective-diffusive transport) Impulse responses for small and large diffusion parameters $\kappa$ and simulation times $T$.}
	\label{tbl:adv_vary_kappa_tf}
\end{figure}

>>>>

% SIAM Article Template
\documentclass[onefignum,onetabnum]{siamart190516}

@@

\begin{figure}
	\centering
	{
		\begin{tabular}{ccc}
			& $T=0.5$ 
			& $T=2.0$ \\
			$\kappa=1.0$e${-4}$  & \includegraphics[scale=0.12, valign=c]{impulse_response_P_0.3,0.6__T0.5_K1.e-4.png} 
			& \includegraphics[scale=0.12, valign=c]{impulse_response_P_0.3,0.6__T2.0_K1.e-4.png} \\
			$\kappa=1.0$e${-3}$ & \includegraphics[scale=0.12, valign=c]{impulse_response_P_0.3,0.6__T0.5_K1.e-3.png} 
			& \includegraphics[scale=0.12, valign=c]{impulse_response_P_0.3,0.6__T2.0_K1.e-3.png}
		\end{tabular}
	}
	\caption{(Advective-diffusive transport) Impulse responses for small and large diffusion parameters $\kappa$ and simulation times $T$.}
	\label{tbl:adv_vary_kappa_tf}
\end{figure}
